%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{scrartcl}
\usepackage[utf8]{inputenc}

\reversemarginpar % Move the margin to the left of the page

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters,pdfspacing]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document
\usepackage{graphicx}

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox} % Set the width of the date box in each block
\setlength{\datebox}{30mm}

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}
%----------------------------------------------------------------------------------------

\begin{document}

\pagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Damian Świstowski}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading


\NewEntry{email}{\href{mailto:damian@swistowski.org}{damian@swistowski.org}} % Email address

% \NewEntry{website}{\href{http://www.johnsmith.com}{http://www.johnsmith.com}} % Personal website
\date{}
\NewEntry{phone}{+44 7402 64 28 69} % Phone number(s)

%\NewEntry{address}{}
% \vspace{1em} % Extra white space between the personal information section and goal

% \noindent\spacedlowsmallcaps{Goal}\vspace{1em} % Goal heading, could be used for a quotation or short profile instead

\vspace{1em}

\Description{I am a staff-level software engineer with 15+ years of experience building reliable backend systems, data platforms, and distributed applications. I have worked across startups and large organisations, delivering everything from web applications to large-scale enterprise platforms. I am a polyglot programmer with particular expertise in Python, TypeScript, and distributed systems.
} % Description of yourself

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------




\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{Oct 2025 - Present}{Staff Software Engineer}


\Description{\MarginText{Figment\\\textsc{London / Remote}}Leading the integration of Rated indexers into Figment infrastructure, aligning architecture and delivery with the broader platform strategy.
}

\Description{Driving the migration of existing indexers to the new Figment stack, including the move from ECS to Kubernetes and from an in-house Bytewax-based execution model to Temporal.
}

\Description{Improving the reliability, maintainability, and scalability of indexing systems used to support blockchain data products.
}


\Description{python $\sbullet$ postgresql $\sbullet$ web3 $\sbullet$ temporal $\sbullet$ BigQuery $\sbullet$ terraform $\sbullet$ ECS $\sbullet$ kubernetes}
%------------------------------------------------

\NewEntry{Oct 2024 - Oct 2025}{Staff Software Engineer}


\Description{\MarginText{Rated Labs Ltd\\\textsc{London / Remote}}Architected and led a major refactor of the Ethereum indexer, rewriting the codebase to improve observability, testability, and horizontal scalability.
}

\Description{Improved the operational maturity of other indexers through better deployment automation, monitoring, and production support practices.
}

\Description{Built a reusable framework for indexers and data pipelines, including tooling to generate and synchronize integrations for BigQuery, Protobuf, and Aurora.
}


\Description{python $\sbullet$ postgresql $\sbullet$ web3 $\sbullet$ bytewax $\sbullet$ BigQuery $\sbullet$ ansible $\sbullet$ ECS}
%------------------------------------------------

\NewEntry{Oct 2023 - Oct 2024}{Software Engineer}


\Description{\MarginText{Genie AI\\\textsc{Remote}}Built backend services with a strong emphasis on testability, maintainability, and delivery speed.
}

\Description{Automated the continuous delivery pipeline and simplified dependency build processes to improve developer efficiency.
}

\Description{Integrated platform components with multiple exchanges and blockchains, including Deribit, OKX, and Solana.
}

\Description{Expanded the asset metrics portfolio while keeping calculation pipelines efficient and scalable.
}


\Description{python $\sbullet$ fastapi $\sbullet$ kubernetes $\sbullet$ terraform $\sbullet$ postgresql $\sbullet$ typescript $\sbullet$ react $\sbullet$ graphql $\sbullet$ rest api}
%------------------------------------------------

\NewEntry{2022 - 2023}{Staff Engineer}


\Description{\MarginText{Babylon Health\\\textsc{London}}Designed and delivered the third generation of Babylon's conversation platform for asynchronous messaging.
}

\Description{Developed a GraphQL API for northbound traffic and a REST API for east-west service communication.
}

\Description{Created Conversation Platform Test Runner (COPTeR), a domain-specific testing tool that enabled stable, product-wide acceptance testing and integrated smoothly with Babylon's testing infrastructure.
}


\Description{python $\sbullet$ fastapi $\sbullet$ kubernetes $\sbullet$ elasticsearch $\sbullet$ kafka $\sbullet$ typescript $\sbullet$ react native $\sbullet$ graphql $\sbullet$ rest api}
%------------------------------------------------

\NewEntry{2020 - 2022}{Engineering Manager}


\Description{\MarginText{Babylon Health\\\textsc{London}}Managed 3 to 6 direct reports and supported team growth through coaching, pairing, and knowledge-sharing.
}

\Description{Worked closely with product managers and stakeholders to define roadmap priorities and align delivery with business goals.
}

\Description{Led the seamless transition from the first-generation conversation platform to the second generation without service disruption.
}

\Description{Maintained high engineering standards, including SSDLC compliance and strong operational practices.
}

\Description{Balanced short-term delivery with long-term technical sustainability, helping the team avoid unnecessary technical debt.
}


\Description{python $\sbullet$ flask $\sbullet$ kubernetes $\sbullet$ terraform $\sbullet$ postgres $\sbullet$ redis $\sbullet$ kafka $\sbullet$ typescript $\sbullet$ rest api}
%------------------------------------------------

\NewEntry{2019 - 2020}{Senior Software Engineer}


\Description{\MarginText{Babylon Health\\\textsc{London}}Designed the migration strategy from a first-generation monolith to a second-generation microservices architecture for the conversation platform.
}

\Description{Built CLI tooling to simplify internal and external integrations with the Conversation Platform.
}


\Description{python $\sbullet$ flask $\sbullet$ kubernetes $\sbullet$ terraform $\sbullet$ postgresql $\sbullet$ redis $\sbullet$ kafka $\sbullet$ rest api}
%------------------------------------------------

\NewEntry{2019}{Senior Software Engineer}


\Description{\MarginText{B2C2\\\textsc{London}}Designed and built a trade history collection system for market data processing.
}

\Description{Implemented a REST API crawler as a cloud task and processed raw data through stateless workflows.
}

\Description{Integrated with multiple exchange APIs to support data ingestion.
}


\Description{python $\sbullet$ aws $\sbullet$ lambda $\sbullet$ sqs $\sbullet$ elasticache}
%------------------------------------------------

\NewEntry{2017 - 2019}{Senior Python Developer}


\Description{\MarginText{Springer Nature\\\textsc{London}}Built and improved internal CI/CD systems and engineering tooling.
}

\Description{Led migration efforts from legacy Python 2 systems to Python 3.
}

\Description{Defined simplified build pipelines to help other teams improve delivery workflows.
}

\Description{Developed deployment tooling for Cloud Foundry environments.
}


\Description{python $\sbullet$ OpenStack $\sbullet$ CloudFoundry $\sbullet$ celery}
%------------------------------------------------

\NewEntry{2015 - 2017}{Senior Engineer}


\Description{\MarginText{Shortlist\\\textsc{San Francisco / Remote}}Built backend services for a workforce management platform.
}

\Description{Partnered with frontend engineers to design and deliver a robust REST API.
}

\Description{Designed and implemented the core data model for the system.
}


\Description{python $\sbullet$ django $\sbullet$ postgresql $\sbullet$ django rest framework $\sbullet$ javascript $\sbullet$ angular $\sbullet$ rest api}
%------------------------------------------------

\NewEntry{2012 - 2015}{Senior Python Developer}


\Description{\MarginText{ZedMedia\\\textsc{Globally / Remote}}Maintained and extended Django-based applications serving editorial and publishing workflows.
}

\Description{Implemented a scoring algorithm for ranking articles across different sections of the service.
}

\Description{Extended and maintained database models supporting product evolution.
}

\Description{Developed tooling to support A/B testing and experimentation.
}


\Description{python $\sbullet$ django $\sbullet$ postgresql $\sbullet$ javascript $\sbullet$ perl}
%------------------------------------------------

\NewEntry{2010 - 2012}{Senior Python Developer}


\Description{\MarginText{Intelligent Elite\\\textsc{Barcelona}}Built an A/B testing suite with detailed user behaviour analytics.
}

\Description{Improved the platform's mailing system and supporting infrastructure.
}


\Description{python $\sbullet$ django $\sbullet$ postgresql $\sbullet$ solr $\sbullet$ mongodb}
%------------------------------------------------

\NewEntry{2008 - 2010}{Python Developer}


\Description{\MarginText{OMS\\\textsc{Bielsko-Biała, Poland}}Designed and implemented a production management system.
}

\Description{Managed and supported a team of 4 junior engineers.
}


\Description{python $\sbullet$ django $\sbullet$ mysql}
%------------------------------------------------

\NewEntry{2007 - 2008}{Junior PHP Developer}


\Description{\MarginText{Gery Design\\\textsc{Wrocław, Poland}}Migrated legacy PHP projects to Django.
}

\Description{Maintained and optimized existing client projects.
}


\Description{php $\sbullet$ javascript $\sbullet$ python $\sbullet$ django}
%------------------------------------------------


\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}


\NewEntry{2005 - 2007}{The University of Silesia, Katowice}

\Description{\MarginText{Master of Computer Science}\ \ $\cdotp$\ \ Computer Science and Materials Science\newline
Thesis: \textit{Particle Swarm Optimization in function minimization}}

%------------------------------------------------

\NewEntry{2002 - 2005}{The University of Silesia, Katowice}

\Description{\MarginText{Bachelor of Computer Science}\ \ $\cdotp$\ \ Computer Science and Materials Science\newline
Thesis: \textit{Developing an electronic repository for undergraduate theses}}

%------------------------------------------------



%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Publications}\vspace{1em}


\NewEntry{2006}{Comparative Study: ACO and EC for TSP}

\Description{\MarginText{kaeiog}The paper focuses on the Traveling Salesman Problem solved using evolutionary and ACO algorithms.
}

%------------------------------------------------



%------------------------------------------------

\vspace{1em} % Extra space between major sections


%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Other Information}\vspace{1em}

\Description{\MarginText{Communication Skills}
2019\ \ $\cdotp$\ \ PyCon UK\newline
cattrs: how to use it with REST microservices

}

%------------------------------------------------

\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

%------------------------------------------------


\Description{\MarginText{Interests}Hiking\ \ $\cdotp$\ \ Social dancing\ \ $\cdotp$\ \ Cooking\ \ $\cdotp$\ \ Video games}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}